### 2018-05-18 doc/large_strain.tex
Add some text outlining the constitutive model

@@

@@

TODO: question to asnwer -- how much to cache? At least detF ^ {2/3}. Other options is stress and strain at quadrature points.
Run benchmarks and see.

>>>>

%\DeclareMathOperator{\det}{det}
\DeclareMathOperator{\trace}{tr}
\newcommand{\diff}{\mathop{}\!\mathrm{d}}

@@

\subsection{Constitutive modelling}

Neo-Hookean model
\begin{gather}
\psi \left( \mathbf{C} \right)
  = \frac{\mu}{2} \left[ \trace{\mathbf{C}} - \trace{\mathbf{I}} - 2 \ln\left( J \right) \right]
  - \lambda \ln^{2}\left( J \right)
\end{gather}
where $\mu$ and $\lambda$ respectively denote the shear modulus and Lam\'{e} parameter,
and the volumetric Jacobian $J = \det\left(\mathbf{F}\right) = \sqrt{\det\left(\mathbf{C}\right)}$.
\begin{gather}
\frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}}
  = \frac{\mu}{2} \mathbf{I} - \frac{1}{2} \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{C}^{-1}
\end{gather}
\begin{gather}
\frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}}
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \left[ - \frac{d \mathbf{C}^{-1}}{d \mathbf{C}} \right]
  + \frac{\lambda}{2} \mathbf{C}^{-1} \otimes \mathbf{C}^{-1}
\end{gather}

Denoting $\chi\left( \bullet \right)$ as the Piola transformation, which implies
\begin{gather}
\chi\left( \mathbf{A} \right)_{ij}
  = F_{iA} A_{AB} F_{jB} \\
\chi\left( \boldsymbol{\mathcal{A}} \right)_{ijkl}
  = F_{iA} F_{jB} \mathcal{A}_{ABCD} F_{kC} F_{lD} 
\end{gather}
for rank-2 and rank-4 tensors $\mathbf{A}$ and $\boldsymbol{\mathcal{A}}$, then the Kirchhoff stress and its associated material tangent are
\begin{gather}
\boldsymbol{\tau}
  \equiv J \boldsymbol{\sigma}
  = \chi\left( 2 \frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}} \right)
  = \mu \mathbf{b} - \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{I}
\end{gather}
and 
\begin{gather}
J \boldsymbol{\mathcal{C}}
  = \chi\left( 4 \frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}} \right)
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \boldsymbol{\mathcal{S}}
  + \frac{\lambda}{2} \mathbf{I} \otimes \mathbf{I}
\end{gather}
where $\boldsymbol{\mathcal{S}}$ is the fourth-order symmetric identity tensor.
The action that $J \boldsymbol{\mathcal{C}}$ performs when contracted with an arbitrary rank-2 symmetric tensor is therefore
\begin{gather}
J \boldsymbol{\mathcal{C}} : \left( \bullet \right)
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \left( \bullet \right)
  + \frac{\lambda}{2} \trace\left( \bullet \right) \mathbf{I}
\end{gather}

@@

TODO: question to asnwer -- how much to cache? At least $detF ^ {2/3}$. Other options is stress and strain at quadrature points.
Run benchmarks and see.
